Reformulating phylogenetic mixed models to improve flexibility and speed

### 2022-08-09 response.md

2. In the paper, the authors replace the package MCMCglmm by the package brms. Although the implementation of MCMCglmm is not as efficient as brms, the complexity of MCMCglmm is linear with respect to the number of species while brms should be cubic (since it doesn't have a special method to avoid matrix inversion). It may be a good idea to add a simulation with a series of trees from dozens to thousands of species for showing the scalability of these methods (including MCMCglmm).

**We have now added MCMCglmm to our set of simulation. For our simple simulation test, MCMCglmm was generally faster than brms, although both Bayesian approaches (MCMCglmm/brms) were still significantly slower than frequentist methods, and scaled slightly worse.**

3. The models in simulations are not sufficiently described. What are the formulae for the phylogenetic random intercept variance, phylogenetic random slope variance, and covariance between phylogenetic random intercept and slope, and so on? Do they depend on the phylogenetic tree? The authors provide a clear explanation for how their proposed method can be applied to the standard phylogenetic regression (equation 1) but do not include it in the simulation section. I suggest the authors add this model to the simulation part for illustrating the applicability of their proposed method for this simple case.

**We have to admit that we are confused by this comment. We tried to clearly indicate that the simulations follow precisely the same structures as we are using for estimation, which is described in detail in the first section ...**

### 2022-08-09 phyloglmm_ms_resubmit.tex
more TODO etc

\bmb{ML: please check notation; in particular, is $\sigma^2_{\mathrm{phy}}$ correct??}
Compared to the single--group model, the multi-group simulation model has five additional random effect parameters: predictor-level ($\sigma^2_{\mathrm{sp_{slope}}}$) and intercept-level ($\sigma^2_{\mathrm{sp_{int}}}$) among-species variances;  their covariance ($\sigma_{\mathrm{sp_{int-slope}}}$);  among-group variation in the intercept ($\sigma^2_{\mathrm{group}}$); and variation among species-group combinations in the intercept ($\sigma^2_{\mathrm{phy}}$).
Because each species has multiple observations we can distinguish variation among species from residual variation, and thus we can include predictor-level and intercept-level random effects of species.
Variance in the intercept of species--group interactions ($\sigma^2_{\mathrm{phy}}$) describes whether the species within a group have more similar responses on average than expected by chance, equivalent to phylogenetic attraction \citep{helmus2007separating}.

>>>>

\bmb{ML: please check notation; in particular, is $\sigma^2_{\mathrm{phy}}$ correct for the sp-group variance??}
Compared to the single--group model, the multi-group simulation model has five additional random effect parameters: predictor-level ($\sigma^2_{\mathrm{sp_{slope}}}$) and intercept-level ($\sigma^2_{\mathrm{sp_{int}}}$) among-species variances;  their covariance ($\sigma_{\mathrm{sp_{int-slope}}}$);  among-group variation in the intercept ($\sigma^2_{\mathrm{group}}$); and variation among species-group combinations in the intercept ($\sigma^2_{\mathrm{phy}}$).
Because each species has multiple observations we can distinguish variation among species from residual variation, and thus we can include predictor-level and intercept-level random effects of species.
Variance in the intercept of species--group interactions ($\sigma^2_{\mathrm{phy}}$) describes whether the species within a group have more similar responses on average than expected by chance, equivalent to phylogenetic attraction \citep{helmus2007separating}.
